---
title: "Tidy Asset Pricing"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This note is a replication of [Tidy Asset Pricing](https://christophscheuch.github.io/post/asset-pricing/crsp-sample/) by Christoph Scheuch.

- Here is the options that run through the entire note
```{r}
# conducts heavy (> 1hr) computation
heavy <- FALSE   

# restrict sample until Dec 2019, consistent with
# the original note
sample_restrict <- FALSE   
```

# Part I: The CRSP Sample 
- Packages
```{r}
pacman::p_load(tidyverse, scales, viridis, vroom,
               lubridate, here, slider, moments, 
               corrr, kableExtra, broom, sandwich,
               matsuno, FamaFrench)
```

- Load data
```{r}
tbl.crsp_msf <- vroom(file = here("input/CRSP_msf.csv"),
                      col_types = cols(.default = col_character()),
                      col_select = c(PERMNO, date, RET, SHROUT, ALTPRC,
                                     EXCHCD, SHRCD, SICCD, DLRET, DLSTCD))
colnames(tbl.crsp_msf) <- str_to_lower(colnames(tbl.crsp_msf))
```

- Make sure that all relevant vars are correctly parsed
```{r}
tbl.crsp_monthly <- tbl.crsp_msf %>% 
  transmute(permno = as.integer(permno),       # security identifier
            date = ymd(date),                  # date of the observation
            month = floor_date(date, "month"), # month identifier
            ret = as.numeric(ret) * 100,       # return (in percent)
            shrout = as.numeric(shrout),       # shares outstanding (in thousands)
            altprc = as.numeric(altprc),       # last traded price in a month
            exchcd = as.integer(exchcd),       # exchange code
            shrcd = as.integer(shrcd),         # share code
            siccd = as.integer(siccd),         # industry code
            dlret = as.numeric(dlret) * 100,   # delisting return (in percent)
            dlstcd = as.integer(dlstcd)        # delisting code
  )
rm(tbl.crsp_msf)
```

- Focus on US-based common stocks
```{r}
tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  filter(shrcd %in% c(10, 11))
```

- Remove duplicates
```{r}
NROW(tbl.crsp_monthly)
tbl.crsp_montly_duplicate <- tbl.crsp_monthly %>%
  group_by_all() %>%
  filter(n() > 1) %>% 
  ungroup()
cat("The number of duplicated records are " %+%
      NROW(tbl.crsp_montly_duplicate))
cat("The percentage of duplicated records are " %+% 
      (round(NROW(tbl.crsp_montly_duplicate)/NROW(tbl.crsp_monthly), 4) * 100) %+% "%")

# remove duplicates 
tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  distinct(permno, date, .keep_all = TRUE)
```

- Compute market cap.
  - `shrout` is in thousands, so`mktcap` is in millions of dollars.
  - We adjust the market cap by cpi.
```{r}
tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  mutate(mktcap = abs(shrout * altprc) / 1000,
         mktcap = if_else(mktcap == 0, NA_real_, mktcap))

tbl.cpi_raw <- readr::read_csv(here("input/CPIAUCNS.csv"))

tbl.cpi <- tbl.cpi_raw %>% 
  filter(DATE <= max(tbl.crsp_monthly$date)) %>% 
  transmute(month = floor_date(DATE, "month"),
            cpi = CPIAUCNS) %>% 
  arrange(month) %>% 
  mutate(cpi = cpi/last(cpi))

tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  left_join(tbl.cpi, by = c("month")) %>% 
  mutate(mktcap_cpi = mktcap / cpi)
```

- Create stock exchange category.
  - The value `3*` means when-issued trading
```{r}
tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  mutate(exchange = case_when(exchcd %in% c(1, 31) ~ "NYSE",
                              exchcd %in% c(2, 32) ~ "AMEX",
                              exchcd %in% c(3, 33) ~ "NASDAQ",
                              TRUE ~ "other"))
```

- Number of securities by exchange
```{r}
fig.securities <- tbl.crsp_monthly %>% 
  group_by(exchange, date) %>% 
  summarise(n = n(), mktcap_cpi = mean(mktcap_cpi, na.rm = TRUE)) %>% 
  ungroup() %>% 
  ggplot(aes(date, n, colour = exchange, linetype = exchange)) +
  geom_point(aes(size = mktcap_cpi)) +
  labs(x = NULL, y = NULL, color = NULL, linetype = NULL,
       title = "Montly number of securities by exchange") + 
  scale_x_date(expand = c(0, 0), date_breaks = "10 years", date_labels = "%Y") +
  scale_y_continuous(labels = comma, breaks = pretty_breaks()) +
  theme_classic() +
  scale_color_viridis_d()
fig.securities
```

- Industry variable by CPI
```{r}
tbl.crsp_monthly <- tbl.crsp_monthly %>%
  mutate(industry = case_when(
    siccd >= 1 & siccd <= 999 ~ "Agriculture",
    siccd >= 1000 & siccd <= 1499 ~ "Mining",
    siccd >= 1500 & siccd <= 1799 ~ "Construction",
    siccd >= 2000 & siccd <= 3999 ~ "Manufacturing",
    siccd >= 4000 & siccd <= 4999 ~ "Transportation",
    siccd >= 5000 & siccd <= 5199 ~ "Wholesale",
    siccd >= 5200 & siccd <= 5999 ~ "Retail",
    siccd >= 6000 & siccd <= 6799 ~ "Finance",
    siccd >= 7000 & siccd <= 8999 ~ "Services",
    siccd >= 9000 & siccd <= 9999 ~ "Public",
    TRUE ~ "Missing"))
```

- Industry distribution
```{r}
fig.industries <- tbl.crsp_monthly %>% 
  filter(!is.na(industry)) %>% 
  count(industry, date) %>% 
  ggplot(aes(date, n, color = industry, linetype = industry)) + 
  geom_line(size = 1) +
  labs(x = NULL, y = NULL, color = NULL, linetype = NULL, 
       title = "Montly number of securities by industry") +
  scale_x_date(expand = c(0, 0), date_breaks = "10 years", date_labels = "%Y") +
  scale_y_continuous(labels = comma, breaks = pretty_breaks()) + 
  theme_classic() +
  scale_color_viridis_d()
fig.industries
```

- Compute return with taking delisting into account
```{r}
tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  mutate(ret_adj = case_when(is.na(dlstcd) ~ ret,
                             !is.na(dlstcd) & !is.na(dlret) ~ dlret,
                             dlstcd %in% c(500, 520, 580, 584) | 
                              (dlstcd >= 551 & dlstcd <= 574) ~ -30,
                             TRUE ~ -100))

summary(select(tbl.crsp_monthly, ret, ret_adj))
```

- Market return by CRSP
```{r}
tbl.crsp_si <- read_csv(here("input/crsp_si.csv")) 
colnames(tbl.crsp_si) <- str_to_lower(colnames(tbl.crsp_si))

tbl.crsp_monthly_market <- tbl.crsp_si %>% 
  transmute(month = floor_date(ymd(date), "month"),
            vwretd = vwretd * 100,
            ewretd = ewretd * 100)

tbl.crsp_monthly <- tbl.crsp_monthly_market %>% 
  left_join(tbl.crsp_monthly, by = "month")
```

- Risk free returns by French
```{r, message = FALSE}
tbl.factors_ff_monthly <-
  read_csv(here("input/F-F_Research_Data_Factors.csv"),
           skip = 3,
           col_types = c("i", "d", "d", "d", "d")) %>% 
  rename(date = 1) %>% 
  mutate(digits = floor(log10(date)) + 1) %>% 
  filter(digits == 6) %>%    # delete yearly data
  transmute(month = floor_date(ymd(paste0(date, "01")), "month"),
            rf_ff = as.numeric(RF),
            mkt_ff = as.numeric(`Mkt-RF`) + as.numeric(RF),
            smb_ff = as.numeric(SMB),
            hml_ff = as.numeric(HML))

tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  left_join(tbl.factors_ff_monthly, by = "month")
```

- Plot cumulative returns
```{r}
tbl.market <- tbl.crsp_monthly %>% 
  distinct(date, vwretd, ewretd, mkt_ff) %>% 
  pivot_longer(-date, names_to = "portfolio", values_to = "return") %>%
  na.omit() %>% 
  group_by(portfolio) %>% 
  arrange(date) %>% 
  mutate(cum_return = cumsum(log(1 + return/100))) %>% 
  ungroup()

fig.market <- tbl.market %>% 
  mutate(portfolio = case_when(
    portfolio == "vwretd" ~ "CRSP (Value-Weighted)",
    portfolio == "ewretd" ~ "CRSP (Equal-Weighted)",
    portfolio == "mkt_ff" ~ "MKT (Fama-French)")) %>% 
  ggplot(aes(x = date, y = cum_return, colour = portfolio)) + 
  geom_line(size = 1, alpha = .7) +
  labs(x = NULL, y = NULL, colour = NULL, 
       title = "Cumulative log return for different market factors") +
  scale_x_date(expand = c(0, 0), date_breaks = "10 years", date_labels = "%Y") + 
  scale_y_continuous(labels = percent, breaks = pretty_breaks()) +
  theme_classic() +
  scale_color_viridis_d()
fig.market
```

- Future return
    - We cannot simply use `lead()` to creat 1-month future return. This is because some records have jumps in month. For example, if `2020-02-01` has `2020-04-01` as the next record, `lead(month)` wrongly indicate the April return as a one-month future return of the February return. On the other hand, the method below correctly gives `NA` as a one-month future return of the February return. 
```{r}
# one way
tbl.crsp_monthly_f1 <- tbl.crsp_monthly %>%
  transmute(permno = permno,
            month = floor_date(date, "month") %m-% months(1),
            ret_excess_f1 = ret - rf_ff,
            ret_adj_excess_f1 = ret_adj - rf_ff,
            mkt_ff_excess_f1 = mkt_ff - rf_ff)

tbl.crsp_monthly <- tbl.crsp_monthly %>%
  left_join(tbl.crsp_monthly_f1, by = c("permno", "month"))
```

- Finally, we check the descriptive statistics and save data.
```{r}
tbl.crsp_monthly <- tbl.crsp_monthly %>% 
  arrange(permno, month)

write_rds(tbl.crsp_monthly, here("middle/crsp_monthly.rds"))

summary(tbl.crsp_monthly)
```

- Now that we saved the data, we clear all objects
```{r}
rm(tbl.crsp_monthly, tbl.crsp_monthly_f1)
```

# Part II: Beta and Stock Return
- In this section, we estimate $beta$ and examine its relation to stock returns.
- First, we read the data prepared in the previous section and compute thee excess returns
```{r}
tbl.crsp_monthly <- read_rds(here("middle/crsp_monthly.rds")) %>% 
  mutate(ret_adj_excess = ret_adj - rf_ff, 
         mkt_excess = mkt_ff - rf_ff) %>% 
  select(permno, month, mkt_excess, ret_adj_excess)
```


## Estimation
- Now, we estimate beta for all stocks
```{r}
# # dtplyr (sequential; slow)
# system.time(
# tbl.betas_monthly <- dtplyr::lazy_dt(tbl.crsp_monthly) %>%
#   group_by(permno) %>%
#   arrange(month) %>%
#   mutate(
#     beta_1y = FamaFrench::rolling_capm_regression(
#       cur_data(), 
#       window = 12,
#       freq = "monthly"),
#     beta_2y = FamaFrench::rolling_capm_regression(
#       cur_data(), 
#       window = 24,
#       freq = "monthly"),
#     FamaFrench::rolling_capm_regression(
#       cur_data(), 
#       window = 36,
#       freq = "monthly"),
#     FamaFrench::rolling_capm_regression(
#       cur_data(), 
#       window = 60,
#       freq = "monthly")) %>%
#   ungroup() %>% 
#   collect() %>% 
#   select(permno, month, starts_with("beta"))
# )
```

```{r}
if(heavy){
# parallelized computation
window_vec <- c(12, 24, 36, 60)

# register
library(doParallel)
cl <- parallel::makePSOCKcluster(parallel::detectCores(logical = FALSE))
doParallel::registerDoParallel(cl)

# computation
system.time(
result <- foreach(
  i = seq_along(window_vec),
  .packages = c('dplyr', 'purrr', "slider",
                'FamaFrench','tidyr')
 ) %dopar% {
  dtplyr::lazy_dt(tbl.crsp_monthly) %>%
  group_by(permno) %>%
  arrange(permno, month) %>%
  mutate(beta = rolling_capm_regression(cur_data(), 
                                      window = window_vec[i],
                                      freq = "monthly"),
         window = c("1Y", "2Y", "3Y", "5Y")[i]) %>% 
  ungroup() %>% 
  collect() %>% 
  unnest(beta) %>% 
  select(permno, month, beta, se, window)
  }
)

# kill finished tasks
parallel::stopCluster(cl)

# combine results
tbl.betas_monthly <- bind_rows(result)

# save the data
write_rds(tbl.betas_monthly, here("middle/betas_monthly.rds"))
rm(tbl.betas_monthly)
}
```


- For the monthly data, using `{roll}` package is much faster.
```{r}
# parallelized computation
window_vec <- c(12, 24, 36, 60)

# register
library(doParallel)
cl <- parallel::makePSOCKcluster(parallel::detectCores(logical = FALSE))
doParallel::registerDoParallel(cl)

system.time(
result <- foreach(
  i = seq_along(window_vec),
  .packages = c('dplyr', 'purrr', "slider",
                'FamaFrench','tidyr', 'roll')
  ) %dopar% {
    tbl.crsp_monthly %>% 
      group_by(permno) %>%
      arrange(permno, month) %>%
      summarise(
        roll_rolling_capm_regression(
          cur_data(),
          window = window_vec[i],
          freq = "monthly"),
        window = c("1Y", "2Y", "3Y", "5Y")[i],
        month = month,
        mkt_excess = mkt_excess,
        ret_adj_excess = ret_adj_excess,
        .groups = "drop") %>% 
      ungroup()
  }
)

# kill finished tasks
parallel::stopCluster(cl)

# combine results
tbl.betas_monthly <- bind_rows(result)

# save the data
write_rds(tbl.betas_monthly, here("middle/betas_monthly.rds"))
rm(tbl.betas_monthly, result)
```


## Descriptive statistics
- Now we conduct descriptive analysis of beta.
```{r}
tbl.betas_monthly <- read_rds(here("middle/betas_monthly.rds"))
tbl.crsp_monthly <- read_rds(here("middle/crsp_monthly.rds"))
                             
if(sample_restrict){
  tbl.betas_monthly <- tbl.betas_monthly %>% 
    filter(month <= ymd("2019-12-31"))
  
  tbl.crsp_monthly <- tbl.crsp_monthly %>% 
    filter(month <= ymd("2019-12-31"))
}

tbl.betas <- tbl.crsp_monthly %>% 
  select(permno, month, ends_with("f1"), 
         mktcap, mktcap_cpi, exchange) %>% 
  left_join(tbl.betas_monthly, by = c("permno", "month"))

# wide data that is consistent with the original note
tbl.betas_wide <- tbl.betas %>% 
  select(permno, month, beta, window) %>% 
  pivot_wider(names_from = window,
              values_from = beta,
              names_prefix = "beta_")

rm(tbl.betas_monthly)
```

- Plot the share of stock that are used in beta computation in each month.
```{r}
tbl.coverage <- tbl.betas %>% 
  select(month, permno, beta, window) %>% 
  group_by(month, window) %>% 
  summarise(share = n_distinct(permno[!is.na(beta)]) /
              n_distinct(permno),
            .groups = "drop") 

fig.coverage <- tbl.coverage %>% 
  mutate(window = factor(window, 
                         levels = c("1Y", "2Y", "3Y", "5Y"))) %>% 
  ggplot(aes(month, share, colour = window)) + 
  geom_line() +
  labs(x = NULL, y = NULL, color = NULL, linetype = NULL,
       title = "Monthly share of stocks with beta estimate") +
  scale_x_date(expand = c(0, 0), date_breaks = "10 years", 
               date_labels = "%Y") +
  scale_y_continuous(labels = percent, breaks = pretty_breaks()) +
  theme_classic() +
  scale_color_viridis_d()
fig.coverage
```
- How many of estimates are credible (t-value >= 2.0)?
```{r}
tbl.betas %>% 
  select(month, permno, beta, window, se) %>% 
  mutate(t_val = beta / se) %>% 
  na.omit() %>% 
  group_by(month, window) %>% 
  summarise(share = n_distinct(abs(t_val) >= 2) / n_distinct(t_val),
            .groups = "drop") %>% 
  ggplot(aes(month, share, colour = window)) + 
  geom_line() +
  labs(x = NULL, y = NULL, color = NULL, linetype = NULL,
       title = "Monthly share of stocks with t-value >= 2") +
  scale_x_date(expand = c(0, 0), date_breaks = "10 years", 
               date_labels = "%Y") +
  scale_y_continuous(labels = percent, breaks = pretty_breaks()) +
  theme_classic() +
  scale_color_viridis_d()
```

- Next, we see the distribution of betas
```{r}
# time series plot
tbl.betas %>% 
  select(permno, month, beta, window) %>% 
  group_by(month, window) %>% 
  summarise(beta_mean = mean(beta, na.rm = TRUE),
            beta_sd = sd(beta, na.rm = TRUE),
            .groups = "drop") %>% 
  mutate(upper = beta_mean + 1.96 * beta_sd,
         lower = beta_mean - 1.96 * beta_sd) %>% 
  ggplot(aes(month, beta_mean)) + 
  geom_line() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_ribbon(aes(ymax = upper, ymin = lower), alpha = .5) +
  facet_wrap(~ window, scales = "free") +
  theme_classic()
```

```{r}
# Histogram
tbl.betas %>% 
  select(permno, month, beta, window) %>% 
  ggplot(aes(x = beta, fill = window)) +
  geom_density(alpha = .7) + 
  coord_cartesian(xlim = c(-2, 4)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  facet_wrap(~window) +
  theme_classic()
```
- Now, the descriptive statistics.
    - The reason why 5-year window has more `n` than 3-year window is that we do not require monthly data to be consecutive. 
    - If there is a jump in the monthly return data used in the regression, as the horizon gets longer, it is more likely to satisfied the sample size requirement (>24). 
```{r}
# Descriptive stat
tbl.betas_ts <- tbl.betas %>% 
  select(month, beta, window) %>% 
  group_by(window, month) %>% 
  na.omit() %>% 
  summarise(mean = mean(beta),
            sd = sd(beta),
            skew = skewness(beta),
            kurt = kurtosis(beta),
            min = min(beta),
            q05 = quantile(beta, 0.05),
            q25 = quantile(beta, 0.25),
            q50 = quantile(beta, 0.50),
            q75 = quantile(beta, 0.75),
            q95 = quantile(beta, 0.95),
            max = max(beta),
            n = n(),
            .groups = "drop")

# summarise across month
tbl.betas_summary <- tbl.betas_ts %>% 
  select(-month) %>% 
  group_by(window) %>% 
  summarise(across(.cols = everything(),
                   .fns = ~mean(.x),
                   na.rm = TRUE),
            .groups = "drop") %>% 
  mutate(window = factor(window, 
                         levels = c("1Y", "2Y", "3Y", "5Y"))) %>% 
  arrange(window) %>% 
  kable(digits = 2) %>% 
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive"))
tbl.betas_summary
```

- Sanity check
```{r}
# Months that have more n for 5Y than 3Y
tbl.betas_ts %>% filter(window %in% c("3Y", "5Y")) %>% select(window, month, n) %>% arrange(month, window) %>% pivot_wider(names_from = window, values_from = n) %>% filter(`3Y` != `5Y`)

# Look at one example of such month
tbl.betas %>% 
  select(permno, month, beta, window) %>% 
  pivot_wider(id_cols = c(permno, month),
              names_from = window,
              values_from = beta) %>% 
  filter(month == ymd("1931-04-01")) %>% 
  select(permno, month, `3Y`, `5Y`)

tbl.betas %>% filter(permno == 11180, month == ymd("1931-04-01"))

# Look at one firm
x <- tbl.crsp_monthly %>% 
  filter(permno == 11180, month <= ymd("1931-04-01"))
```


## Correlations
- We see cross-sectional correlations between each window of beta
```{r}
tbl.correlations  <- tbl.betas_wide %>% 
  select(-permno) %>% 
  na.omit() %>% 
  group_by(month) %>% 
  nest(betas = starts_with("beta")) %>% 
  mutate(correlations = map(betas,
                            FamaFrench::compute_correlation)) %>% 
  ungroup() %>% 
  select(-betas) %>% 
  unnest(correlations) %>% 
  rename(type = term) %>% 
  mutate(type = factor(type, 
                       levels = paste0("beta_", c(1, 2, 3, 5), "Y"))) %>% 
  group_by(type) %>% 
  summarise(across(starts_with("beta"), mean,
                   na.rm = TRUE))

options(knitr.kable.NA = '')
tab.correlations <- tbl.correlations %>% 
  kable(digits = 2) %>% 
  kable_styling(bootstrap_options = 
                  c("striped", "hover", "condensed", "responsive"))
tab.correlations
```

## Persistence
- We compute the correlation with $\tau$ months of lag.
```{r}
vec.tau <- c(1, 3, 6, 12, 24, 36, 48, 60, 120)

# for all beta
beta_vec <- "beta_" %+% c(1, 2, 3, 5) %+% "Y"

## garbage collection
gc()

## register
library(doParallel)
options(future.globals.maxSize = 1.6 * 1024^3)  # 1.5Gb
cl <- parallel::makePSOCKcluster(4)
doParallel::registerDoParallel(cl)

result <- foreach(
    i = seq_along(beta_vec),
    .packages = c('dplyr', 'purrr', 'tidyr',
                  'FamaFrench','corrr',
                  'lubridate', 'matsuno')
  ) %dopar% {
    compute_persistence(tbl.betas_wide, !!sym(beta_vec[i]), vec.tau,
                        probs = c(.005, .995))
  }

## kill finished tasks
parallel::stopCluster(cl)

# bind the result
tab.persistence <- reduce(result, left_join, by = "tau") %>% 
  kable(digits = 2) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
tab.persistence
```

## Portfolio Analysis
- Does beta positively associated with future returns, as the CAPM predicts?

- We construct portfolios based on estimated betas.
    - Specifically, for stock of company $i$ at time (month) $t$, we estimated beta using the past $j \in \{1, 2, 3, 5\}$ years of data. 
    - Then, for each month and the estimation window $j$, we computed the quantiles to divide the pool of betas in that month and window to portfolios of size `n_portfolios`. 
```{r}
tbl.portfolios <-
  construct_univariate_portfolios(tbl.betas,
                                  nyse_breakpoints = TRUE)
```

- Given the portfolio returns, we test whether the portfolio's return is statistically different from zero.
    - We estimate the mean excess reutnr and the CAPM alpha for each portfolio.
    - We use Newey and West (1987) $t$-stat with $6$ lags to correct for the serial correlation.
```{r}
# Table: Equal weighted
tab.portfolio_returns_ew <- 
  estimate_portfolio_returns(tbl.portfolios, ret_ew) %>%
  reshape_portfolio_returns() %>% 
  kable(digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensxed", "responsive")) %>%
  pack_rows("Estimation Period: 1 Year (Monthly Data) - Equal-Weighted Portfolio Returns", 1, 4) %>%
  pack_rows("Estimation Period: 2 Years (Monthly Data) - Equal-Weighted Portfolio Returns", 5, 8) %>%
  pack_rows("Estimation Period: 3 Years (Monthly Data) - Equal-Weighted Portfolio Returns", 9, 12) %>%
  pack_rows("Estimation Period: 5 Years (Monthly Data) - Equal-Weighted Portfolio Returns", 13, 16) 
tab.portfolio_returns_ew

# Table: Value weighted
tab.portfolio_returns_vw <- 
  estimate_portfolio_returns(tbl.portfolios, ret_vw) %>%
  reshape_portfolio_returns() %>% 
  kable(digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  pack_rows("Estimation Period: 1 Year (Monthly Data) - Value-Weighted Portfolio Returns", 1, 4) %>%
  pack_rows("Estimation Period: 2 Years (Monthly Data) - Value-Weighted Portfolio Returns", 5, 8) %>%
  pack_rows("Estimation Period: 3 Years (Monthly Data) - Value-Weighted Portfolio Returns", 9, 12) %>%
  pack_rows("Estimation Period: 5 Years (Monthly Data) - Value-Weighted Portfolio Returns", 13, 16) 
tab.portfolio_returns_vw
```

- Graphical Result
```{r}
# Equal-weighted
estimate_portfolio_returns(tbl.portfolios, ret_ew) %>% 
  ggplot(aes(x = portfolio, y = estimate, colour = window)) +
  geom_point(aes(shape = window), size = 2) +
  geom_errorbar(aes(ymax = estimate + 1.96 * (estimate / nw_tstat),
                    ymin = estimate - 1.96 * (estimate / nw_tstat))) +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~ type) +
  theme_classic() +
  scale_colour_viridis_d() + 
  ggtitle("Equal-weighted")

# Value-weighted
estimate_portfolio_returns(tbl.portfolios, ret_vw) %>% 
  ggplot(aes(x = portfolio, y = estimate, colour = window)) +
  geom_point(aes(shape = window), size = 2) +
  geom_errorbar(aes(ymax = estimate + 1.96 * (estimate / nw_tstat),
                    ymin = estimate - 1.96 * (estimate / nw_tstat))) +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~ type) +
  theme_classic() +
  scale_colour_viridis_d() + 
  ggtitle("Value-weighted")
```

## Regression Analysis

